\pagestyle{plain}
\chapter[Teaching Experience][Teaching Experience]{Teaching Experience}

\section{Teaching Assistantships}

\textit{Columbia University} \setstretch{1}
\begin{itemize}
\item Fall 2018
	\begin{itemize}
	\item Course Title: Heat Transfer
	\item Instructor of Record: Arvind Narayanaswamy
	\item Teaching Staff: one instructor, one teaching assistant
	\item Student Enrollment: 60 undergraduates
	\item Responsibilities: attend lecture (3 hours weekly), plan \& teach recitation (1.5 hours weekly), hold office hours (3 hours weekly), write homework, quiz, \& exam solutions, and grade quizzes \& exams. 
	\end{itemize}
\item Fall 2017
	\begin{itemize}
	\item Course Title: Senior Design I
	\item Instructor of Record: Fred Stolfi
	\item Teaching Staff: one instructor, one teaching assistant, one grader, three staff mentors
	\item Student Enrollment: 55 undergraduates
	\item Responsibilities: hold office hours (2 hours weekly), manage deliverable submissions, schedule meetings \& presentations for 13 student teams, and provide feedback during design reviews.
	\end{itemize}
\item Fall 2013
	\begin{itemize}
	\item Course Title: Introduction to Mechanics of Fluids
	\item Instructor of Record: Sinisa Vukelic
	\item Teaching Staff: one instructor, two teaching assistants, one grader
	\item Student Enrollment: 39 undergraduates
	\item Responsibilities: attend lecture (3 hours weekly), plan \& teach recitation (1.5 hours weekly), hold office hours (1 hour weekly), and grade homework, quizzes \& exams. 
	\end{itemize}
\end{itemize} \setstretch{2}


\textit{University of Rochester} \setstretch{1}
\begin{itemize}
\item Spring 2013
	\begin{itemize}
	\item Course Title: Thermodynamics
	\item Instructor of Record: John. H. Thomas
	\item Teaching Staff: one instructor, four teaching assistants
	\item Student Enrollment: 73 undergraduates
	\item {\color{red}Responsibilities:}
	\end{itemize}
\item Fall 2012
	\begin{itemize}
	\item Course Title: Introduction to Fluid Dynamics
	\item Instructor of Record: John. H. Thomas
	\item Teaching Staff: one instructor, three teaching assistants
	\item Student Enrollment: 69 undergraduates
	\item {\color{red}Responsibilities:}
	\end{itemize}
\end{itemize} \setstretch{2}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Mentorship}

\textit{Columbia University} \setstretch{1}
\begin{itemize}
\item Fall 2017 to Spring 2018
	\begin{itemize}
	\item {\color{red}Oversaw research project for undergraduate student. Gave feedback and direction of project. Taught how to use equipment and write SOPs.}
	\end{itemize}
\item Summer 2016 to Fall 2016
	\begin{itemize}
	\item {\color{red}Oversaw research project for master's student. Taught how to use equiment, write procedures, gave feedback and direction.}
	\end{itemize}
\end{itemize} \setstretch{2}
